---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ubci

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
[![Travis build status](https://travis-ci.org/mrchypark/ubci.svg?branch=master)](https://travis-ci.org/mrchypark/ubci)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/mrchypark/ubci?branch=master&svg=true)](https://ci.appveyor.com/project/mrchypark/ubci)
[![CRAN status](https://www.r-pkg.org/badges/version/ubci)](https://cran.r-project.org/package=ubci)

The goal of ubci is to get UBCI(UpBit Crypto Index) & Crypto price data form [upbit][upbit].

## Installation

You can install the development version of ubci from [GitHub](https://github.com/mrchypark/ubci) with:

```{r message=FALSE}
source("https://install-github.me/mrchypark/ubci")
```

please check encoding UTF-8 for unix-like os.

```{r}
Sys.getlocale()
```

## Example

### index options

`ubci_index_options()` function return list of index code & descriptions.

```{r}
library(ubci)
ubci_index_options()
```

`ubci_index_options()` function provide lang param for korean descriptions.

```{r}
ubci_index_options(lang="ko")
```


### index

`ubci_index()` function return index data with code, range of date with from/to.

```{r}
loi<-ubci_index_options()
loi$index[1]
ubci_index(loi$index[1])
tail(ubci_index(loi$index[1], from="2018-05-15"))
ubci_index(loi$index[1], to="2018-05-15")
ubci_index(loi$index[1], from="2018-05-10", to="2018-05-15")
```

### crypto price options

`ubci_get_options()` function return list of crypto code & name.

```{r}
ubci_get_options()
```

`ubci_get_options()` function provide lang param for korean name of crypto.

```{r}
ubci_get_options(lang="ko")
```


### crypto price

`ubci_get()` function return crypto prcie data with code, range of date with from/to.

```{r}
loc<-ubci_get_options()
loc$code[1]
ubci_get(loc$code[1])
tail(ubci_get(loc$code[1], from="2018-05-15"))
ubci_get(loc$code[1], to="2018-05-15")
ubci_get(loc$code[1], from="2018-05-10", to="2018-05-15")
```

Session info is below.
```{r}
sessionInfo()
```

Data source license is below.

```
“UBCI 인덱스”
Copyright 2018 두나무(주) All rights reserved.
Powered by 두나무/Upbit
```

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.

[upbit]: https://www.ubcindex.com/home
